Megan's code for Isoviz

### 2023-04-24 temp_code/MS_isoviz_code.Rmd
MS test push
MS update plotting function to consider all junctions

---
title: "Megan's code for Isoviz"
output: html_notebook
---

@@

```{r}
# libraries
require(readr)
require(dplyr)
require(tidyr)
require(magrittr)
require(ggplot2)
require(data.table)
require(stringr)
require(ggpubr)
require(grid)
require(gridExtra)
require(cowplot)
require(Biostrings)
require(rempsyc) # for fancy tables: https://cran.r-project.org/web/packages/rempsyc/vignettes/table.html

@@

Updated Function: Map junction to isoform: Updated to include all junctions and use gencode annotations to mark unique versus common
How do we incorporate expression here since the hESC data is more deeply sequenced- could combine feature counts when we format the leafcutter output
```{r}
# merge with gencode info and predictions from 230411_cas13_paper_figures.Rmd
# we should probably filter these for things like runs of T's, etc like we did when designing the screen
# missing 166- which are guides in Harm's screen
v41_info = read_tsv("~/isoviz/data/gencode_v41_all_junction_guides.txt", col_names = TRUE) %>% 
  mutate(guide_sequence = as.character(guide_sequence)) # 2,255,040
predictions = read_csv("/gpfs/commons/groups/knowles_lab/cas13_share/230414_predictions/combined-corrected-predictions-gencode.csv") %>% 
  select(guide_id, predicted_lfc) # 2,254,874

gencode_intron_all_data = v41_info %>% left_join(predictions, by = "guide_id")
save(gencode_intron_all_data, file = "~/isoviz/data/gencode_intron_all_data.rda")

@@

# map junctions function
# I really don't need the guide info here just the junction info- consider revising and bring the guideRNAs in for another junction
map_all_junctions = function(gene = "ENSG00000100320", cell_type = "hESC"){

  # gencode- this is an updated file containing more junction info
  load(file = "~/isoviz/data/gencode_intron_all_data.rda")

  # filter for gene, for now, no need to filter for protein-coding since this gencode set only contains protein-coding
  # this now contains all guide information for this gene
  gene_iso_data = gencode_intron_all_data %>% filter(grepl(gene, gene_id))

  # join iso data with leafcutter data and mark any unannotated junctions
  # consider cell type
  lfc_clusters = paste0(cell_type, "_all_lfc_junctions")
  load(file = paste0("~/isoviz/data/", lfc_clusters, ".rda"))

  # test
  clusters_table %>% filter(chr == "chr22" & start > 35738735 & end < 36028824) %>% arrange(desc(start))

  # since leafcutter junctions dont have gene annotations, need to combine here first
  gene_cluster = gene_iso_data %>% 
    left_join(clusters_table, by = c("chr", "junc_start" = "start", "junc_end" = "end"))

@@

  # to get information on leafcutter junctions that don't match annotation
  all_gene_clusters = clusters_table %>% filter(cluster.n %in% gene_cluster$cluster.n) %>% 
    left_join(gene_iso_data, by = c("chr", "start" = "junc_start", "end" = "junc_end")) %>%
    filter(is.na(gene_id)) %>% 
    mutate(gene_name = unique(gene_cluster$gene_name), strand = unique(gene_cluster$strand), 
           gene_id = unique(gene_cluster$gene_id), junction_category = "unknown", 
           transcript_isoforms = "unknown", junc_id = paste0("unk", 1:nrow(.))) %>%
    select(chr, junc_start = start, junc_end = end, everything()) %>%
    bind_rows(gene_cluster) %>%
    mutate(junc.counts = ifelse(is.na(cluster.n), 0, junc.counts), cluster.counts = ifelse(is.na(cluster.n), 0, cluster.counts))

  n = all_gene_clusters %>% distinct(cluster.n, junc_id) %>% group_by(cluster.n) %>% 
    mutate(junc.per.cluster = ifelse(is.na(cluster.n), 1, n())) %>% ungroup()

  all_gene_clusters %<>% left_join(n, by = c("cluster.n", "junc_id")) %>%
    mutate(junc.usage = ifelse(junc.counts == 0, 0, round((junc.counts/cluster.counts)*100, digits = 0)), cell_line = paste0(cell_type))

  #test
  all_gene_clusters %>% filter(grepl("209", transcript_isoforms)) %>%
    select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% arrange(junc_start)

  # create list of expressed isoforms
  # the logic is that if an isoform has a fully unique junction with no counts, it is unlikely to be expressed
  # I want to be careful here since some junctions won't be represented because of technical issues so only eliminate isoforms where none of their unique junctions have counts, avoid filtering on partially unique for now
  non_expressed_genes = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% group_by(transcript_isoforms, junction_category) %>%
    mutate(isoform_counts = ifelse(junction_category == "fully_unique", sum(junc.counts), junc.counts)) %>% 
    filter(junction_category == "fully_unique" & isoform_counts == 0) %>% distinct(transcript_isoforms) %>% ungroup()

  uniquely_targetable = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "fully_unique") %>%
    distinct(transcript_isoforms)

  partially_targetable = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "partial_unique") %>%
    distinct(transcript_isoforms)

  output = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>%
    mutate(transcript_targetable = ifelse(transcript_isoforms %in% uniquely_targetable$transcript_isoforms, "Uniquely", 
                                          ifelse(transcript_isoforms %in% partially_targetable$transcript_isoforms, "Partially", "None"))) %>% 
    mutate(isoform_expressed = ifelse(transcript_isoforms %in% non_expressed_genes$transcript_isoforms, "Unlikely", "Likely"))

@@

```{r}
load(file='~/isoviz/data/iso_data_complete.rda')
#df = to_plot

@@

Updated plotting to go with all junctions output
```{r}
# might have to use regtools if I truly want all junctions
load(file='~/isoviz/data/iso_data_complete.rda')
df = test

# plot isoform plus leafcutter clusters
plot_all_junction_to_isoform = function(df, junction_usage = 5, include_common_juncs = FALSE, filter_expressed_isoforms = TRUE){

  # filter here based on input parameters
  if(include_common_juncs == FALSE){
    df %<>% filter(junction_category != "common")
  }

  if(filter_expressed_isoforms == TRUE){
    df %<>% filter(isoform_expressed == "Likely")
  }

@@

  # new code to plot leafcutter cluster info underneath isoform level data
  # aggregate isoform information
  text = df %>% separate(col = transcript_isoforms, into = c("name", "transcript")) %>% 
    mutate(transcript = ifelse(is.na(transcript), "unknown", transcript)) %>%
    group_by(cluster.n, junc_id) %>% 
    arrange(cluster.n, junc_id, transcript) %>%
    mutate(isoforms = paste0(transcript, collapse = ",")) %>%
    select(1:5, junc_id, junction_category, junc.usage, isoforms, junc.per.cluster) %>% distinct() %>% ungroup() %>% 
    mutate(text_plot = paste0(junc.counts, " reads (", junc.usage, "%) : ", isoforms))

  clusters = unique(df$cluster.n)
  introns = df %>% select(-gene_id, -gene_name, -transcript_isoforms) %>% 
    distinct() %>% arrange(cluster.n, junc_start)
  introns$junc.order = 1:nrow(introns)
  introns %<>% left_join(text)

@@

  p2 = ggplot() + 
    geom_rect(data = introns, mapping = aes(xmin = junc_start, xmax = junc_end, ymin = junc.order - 0.2, ymax = junc.order + 0.2, fill = cluster.n)) + 
    geom_text(data = introns, aes(x = junc_end, y = junc.order, label = text_plot), hjust = 0, size = 3) +
    xlim(min_start, max_end) + theme_bw() + 
    xlab("Hg38 Genomic Position (bp)") + ylab("") + 
    geom_text(data = introns, aes(x = Inf, y = junc.order, hjust = 0, label = junc_id), size = 3) + 
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "none", plot.margin = margin(0,1,0,0.1, "in")) +
    coord_cartesian(xlim = c(min_start, max_end), clip = 'off')

  # plot dimenstions based on number of isoforms and junctions
  t = (n + nrow(introns))
  h = t/2
  p1_p2 = plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(n*0.8, nrow(introns)))

@@

ggsave("~/isoviz/plots/rbfox2_test.pdf", width = 8, height = h)

@@

Function to get guide RNA predictions for specific junctions
```{r}
# need to read in count information a different way- this is just a quick and dirty method
# write a function to get expressed junctions/isoforms and call that within functions?
get_guide_predictions = function(gene = "ENSG00000100320", cell_type = "hESC", guides_per_junction = 2){
  load(file = "~/isoviz/data/gencode_intron_all_data.rda")
  gene_guides = gencode_intron_all_data %>% filter(grepl(gene, gene_id))
  gene_name = unique(gene_guides$gene_name)
  top_guides = gene_guides %>% filter(junction_category == "partial_unique" | junction_category == "fully_unique") %>%
    group_by(junc_id) %>% slice_min(predicted_lfc, n = guides_per_junction)

  # filter junctions based on expression or by junc_id- this is just set up to get an example

  output = top_guides %>% filter(junc_id %in% for_guides$junc_id) %>% 
    left_join(for_guides) %>%
    select(Cluster = cluster.n, JuncID = junc_id, Category = junction_category, Counts = junc.counts, Usage = junc.usage,
           Isoforms = isoforms, GuideID = guide_id, GuideSeq = guide_sequence, Prediction = predicted_lfc)

@@

  return(nice_table(output, col.format.custom = 4:5, format.custom = "fun", 
                    title = paste0(gene_name, ": Top ", guides_per_junction, " gRNAs per Junction")))
}

>>>>

---
title: "Megan's code for Isoviz"

---

@@

```{r}
# libraries
require(readr)
require(dplyr)
require(tidyr)
require(magrittr)
require(ggplot2)
require(data.table)
require(stringr)
require(ggpubr)
require(grid)
require(gridExtra)
require(cowplot)
require(Biostrings)
library(ggsci)
require(rempsyc) # for fancy tables: https://cran.r-project.org/web/packages/rempsyc/vignettes/table.html

@@

Updated Function: Map junction to isoform: Updated to include all junctions and use gencode annotations to mark unique versus common
How do we incorporate expression here since the hESC data is more deeply sequenced- could combine feature counts when we format the leafcutter output
Using output from minicutter
```{r}

# aggregated for this function
save(gencode_intron_all_data, file = "~/isoviz/data/gencode_intron_all_data.rda")

@@

# map junctions function
map_all_junctions = function(gene = "ENSG00000100320", cell_type = "hESC"){

  # gencode- this is an updated file containing more junction info
  load(file = "~/isoviz/data/gencode_intron_all_data.rda") # 281,880

  # filter for gene, for now, no need to filter for protein-coding since this gencode set only contains protein-coding
  # this now contains all guide information for this gene
  gene_iso_data = gencode_intron_all_data %>% filter(grepl(gene, gene_id)) # 24

  # join iso data with leafcutter data and mark any unannotated junctions
  # consider cell type
  lfc_clusters = paste0(cell_type, "_all_lfc_junctions")
  load(file = paste0("~/isoviz/data/", lfc_clusters, ".rda")) # juncs_recluster

  # since leafcutter junctions dont have gene annotations, need to combine here first
  juncs_recluster %<>% select(everything(), junc.counts = readcount) %>% group_by(cluster_idx) %>% mutate(cluster.counts = sum(junc.counts)) %>% ungroup()
  gene_cluster = gene_iso_data %>% 
    left_join(juncs_recluster, by = c("chr" = "chrom", "junc_start" = "start", "junc_end" = "end", "strand")) %>%
    arrange(cluster_idx) # 24

  # check minicutter output
  juncs_recluster %>% filter(cluster_idx == "134447")

@@

  # to get information on leafcutter junctions that don't match annotation
  all_gene_clusters = juncs_recluster %>% filter(cluster_idx %in% gene_cluster$cluster_idx) %>% 
    left_join(gene_iso_data, by = c("chrom" = "chr", "start" = "junc_start", "end" = "junc_end", "strand")) %>%
    filter(is.na(gene_id)) %>% 
    mutate(gene_name = unique(gene_cluster$gene_name), strand = unique(gene_cluster$strand), 
           gene_id = unique(gene_cluster$gene_id), junction_category = "unknown", 
           transcript_isoforms = "unknown", junc_id = paste0("unk.", row_number())) %>%
    select(chr = chrom, junc_start = start, junc_end = end, everything()) %>%
    bind_rows(gene_cluster) %>%
    mutate(junc.counts = ifelse(is.na(cluster_idx), 0, junc.counts), cluster.counts = ifelse(is.na(cluster_idx), 0, cluster.counts)) %>%
    arrange(cluster_idx)

  n = all_gene_clusters %>% distinct(cluster_idx, junc_id) %>% group_by(cluster_idx) %>% 
    mutate(junc.per.cluster = ifelse(is.na(cluster_idx), 1, n())) %>% ungroup()

  all_gene_clusters %<>% left_join(n, by = c("cluster_idx", "junc_id")) %>%
    mutate(junc.usage = ifelse(junc.counts == 0, 0, round((junc.counts/cluster.counts)*100, digits = 0)), cell_line = paste0(cell_type))

  #test
  all_gene_clusters %>% filter(grepl("209", transcript_isoforms)) %>% arrange(junc_start)

  # create list of expressed isoforms
  # the logic is that if an isoform has a fully unique junction with no counts, it is unlikely to be expressed
  # I want to be careful here since some junctions won't be represented because of technical issues so only eliminate isoforms where none of their unique junctions have counts, avoid filtering on partially unique for now
  non_expressed_genes = all_gene_clusters %>%
    separate_longer_delim(transcript_isoforms, delim = ",") %>% group_by(transcript_isoforms, junction_category) %>%
    mutate(isoform_counts = ifelse(junction_category == "fully_unique", sum(junc.counts), junc.counts)) %>% 
    filter(junction_category == "fully_unique" & isoform_counts == 0) %>% distinct(transcript_isoforms) %>% ungroup()

  uniquely_targetable = all_gene_clusters %>% 
    separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "fully_unique") %>%
    distinct(transcript_isoforms)

  partially_targetable = all_gene_clusters %>% 
    separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "partial_unique") %>%
    distinct(transcript_isoforms)

  output = all_gene_clusters %>% 
    separate_longer_delim(transcript_isoforms, delim = ",") %>%
    mutate(transcript_targetable = ifelse(transcript_isoforms %in% uniquely_targetable$transcript_isoforms, "Uniquely", 
                                          ifelse(transcript_isoforms %in% partially_targetable$transcript_isoforms, "Partially", "None"))) %>% 
    mutate(isoform_expressed = ifelse(transcript_isoforms %in% non_expressed_genes$transcript_isoforms, "Unlikely", "Likely")) # 135

@@

# Outdated
```{r}
load(file='~/isoviz/data/iso_data_complete.rda')

@@

Updated plotting to go with all junctions output
Now includes minicutter output so all junctions represented
```{r}
load(file='~/isoviz/data/iso_data_complete.rda')
#df = test

# plot isoform plus leafcutter clusters
# add a parameter to only plot a specific junction
plot_all_junction_to_isoform = function(gene = "ENSG00000001167.15", cell_type = "hESC", junction_usage = 5, include_common_juncs = FALSE, filter_expressed_isoforms = TRUE){

  # call map_junction function here
  df = map_all_junctions(gene, cell_type)

  # filter here based on input parameters- also unknown junctions that belong to common junctions
  if(include_common_juncs == FALSE){
    remove_cluster = df %>% filter(junction_category == "common") %>% select(cluster_idx) %>% distinct()
    df %<>% filter(!cluster_idx %in% remove_cluster$cluster_idx)
  }

  if(filter_expressed_isoforms == TRUE){
    df %<>% filter(isoform_expressed == "Likely")

     # create list of expressed transcripts
    expressed_isoforms = df %>% filter(isoform_expressed == "Likely", transcript_isoforms != "unknown") %>% 
      separate(col = transcript_isoforms, into = c("name", "transcript")) %>% select(transcript) %>% distinct() %>%
      arrange(transcript) %>%
      mutate(isoforms = paste0(transcript, collapse = ",")) %>% select(isoforms) %>% distinct()
  }

@@

  # make isoform plot
  p1 = ggplot() +
    geom_segment(aes(x = to_plot_ordered$start, y = to_plot_ordered$trans_order,
                     xend = to_plot_ordered$seg_end, yend = to_plot_ordered$trans_order)) +
    geom_rect(data = to_plot_ordered, mapping = aes(xmin = blockstarts, xmax = blockends, ymin = trans_order - 0.3, ymax = trans_order + 0.3)) +
    xlim(min_start, max_end) + ylim(0,y_max) +
    geom_text(aes(x = Inf, y = to_plot_ordered$trans_order, hjust = -0.1, label = to_plot_ordered$transcript_name), size = 3, check_overlap = TRUE) +
    theme_bw() + ylab("") + xlab("") +
    theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), 
          axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "top", 
          plot.title = element_text(hjust = 0.5), plot.margin = margin(0.1,1,0,0.1, "in")) +
    ggtitle(paste0(cell_type, ": ", name, " Junction to Isoform Map (" , to_plot_ordered$strand[1], " strand )")) + 
    coord_cartesian(xlim = c(min_start, max_end), clip = 'off')

  # new code to plot leafcutter cluster info underneath isoform level data
  # aggregate isoform information
  text = df %>% separate(col = transcript_isoforms, into = c("name", "transcript")) %>% 
    mutate(transcript = ifelse(is.na(transcript), "unknown", transcript)) %>%
    group_by(cluster_idx, junc_id) %>% 
    arrange(cluster_idx, junc_id, transcript) %>%
    mutate(isoforms = paste0(transcript, collapse = ",")) %>%
    select(1:5, junc_id, junction_category, junc.usage, isoforms, junc.per.cluster) %>% distinct() %>% ungroup() %>% 
    mutate(text_plot = paste0(junc.counts, " reads (", junc.usage, "%) : ", isoforms), alpha = junc.usage/100)

  clusters = unique(df$cluster_idx)
  introns = df %>% select(-gene_id, -gene_name, -transcript_isoforms) %>% 
    distinct() %>% arrange(cluster_idx, junc.usage)
  introns %<>% left_join(text)

  # gets rid of gencode partially unique junctions that are common in this cell type (100% usage) 
  if(filter_expressed_isoforms == TRUE){
    remove_junc = introns %>% filter(junc.usage & isoforms %in% expressed_isoforms$isoforms)
    introns %<>% filter(!junc_id %in% remove_junc$junc_id)
  }

  introns$junc.order = 1:nrow(introns)

@@

  p2 = ggplot() + 
    geom_rect(data = introns, mapping = aes(xmin = junc_start, xmax = junc_end, ymin = junc.order - 0.2, ymax = junc.order + 0.2, fill = as.character(cluster_idx), alpha = alpha)) + 
    geom_text(data = introns, aes(x = junc_end, y = junc.order, label = text_plot), hjust = "inward", size = 3) +
    scale_fill_npg() + 
    xlim(min_start, max_end) + theme_bw() + 
    xlab("Hg38 Genomic Position (bp)") + ylab("") + 
    geom_text(data = introns, aes(x = Inf, y = junc.order, hjust = -0.1, label = junc_id), size = 3) + 
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "none", plot.margin = margin(0,1,0,0.1, "in")) +
    coord_cartesian(xlim = c(min_start, max_end), clip = 'off')

  # plot dimenstions based on number of isoforms and junctions
  t = (n + nrow(introns))
  h = t/3

  # p1
  if(n <= 4){
    iso_h = n*1.3
  }else{
    iso_h = n*0.8
  }

  # p2
  if(nrow(introns) > 6){
    junc_h = nrow(introns) * 0.8
  }else{
    junc_h = nrow(introns) * 1.2
  }
  p1_p2 = plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(iso_h, junc_h))

@@

#map_all_junctions("ENSG00000001167.15", cell_type = "hESC")
plot_all_junction_to_isoform("ENSG00000100320", cell_type = "hESC") # RBFOX2
ggsave("~/isoviz/plots/rbfox2_hESC_filtered.png", width = 8, height = 5)

plot_all_junction_to_isoform("ENSG00000001167.15", cell_type = "HEK293") # NFYA
ggsave("~/isoviz/plots/nfya_hek293_filtered.png", width = 8, height = 3)

@@

Function to get guide RNA predictions for specific junctions
```{r}
# merge with gencode info and predictions from 230411_cas13_paper_figures.Rmd
# we should probably filter these for things like runs of T's, etc like we did when designing the screen
# missing 166- which are guides in Harm's screen
v41_info = read_tsv("~/isoviz/data/gencode_v41_all_junction_guides.txt", col_names = TRUE) %>% 
  mutate(guide_sequence = as.character(guide_sequence)) # 2,255,040
predictions = read_csv("/gpfs/commons/groups/knowles_lab/cas13_share/230414_predictions/combined-corrected-predictions-gencode.csv") %>% 
  select(guide_id, predicted_lfc) # 2,254,874

gencode_predictions = v41_info %>% left_join(predictions, by = "guide_id")
#save(gencode_predictions, file = "~/isoviz/data/gencode_predictions.rda")

# need to read in count information a different way- this is just a quick and dirty method
# write a function to get expressed junctions/isoforms and call that within functions?
# some of this is copied from map_all_junctions so should make this a function
junctions = c("junc178149", "junc178148")
junc_list = junctions
get_guide_predictions = function(junc_list, cell_type = "hESC", guides_per_junction = 2){
  load(file = "~/isoviz/data/gencode_predictions.rda")
  filtered_guides = gencode_predictions %>% filter(junc_id %in% junc_list)
  gene_name = unique(filtered_guides$gene_name)
  gene = unique(filtered_guides$gene_id)

  # start function here
  load(file = "~/isoviz/data/gencode_intron_all_data.rda") # 281,880
  gene_iso_data = gencode_intron_all_data %>% filter(grepl(gene, gene_id))

  lfc_clusters = paste0(cell_type, "_all_lfc_junctions")
  load(file = paste0("~/isoviz/data/", lfc_clusters, ".rda")) # juncs_recluster

  # since leafcutter junctions dont have gene annotations, need to combine here first
  juncs_recluster %<>% select(everything(), junc.counts = readcount) %>% group_by(cluster_idx) %>% mutate(cluster.counts = sum(junc.counts)) %>% ungroup()
  gene_cluster = gene_iso_data %>% 
    left_join(juncs_recluster, by = c("chr" = "chrom", "junc_start" = "start", "junc_end" = "end", "strand")) %>%
    arrange(cluster_idx) # 24

  # to get information on leafcutter junctions that don't match annotation
  all_gene_clusters = juncs_recluster %>% filter(cluster_idx %in% gene_cluster$cluster_idx) %>% 
    left_join(gene_iso_data, by = c("chrom" = "chr", "start" = "junc_start", "end" = "junc_end", "strand")) %>%
    filter(is.na(gene_id)) %>% 
    mutate(gene_name = unique(gene_cluster$gene_name), strand = unique(gene_cluster$strand), 
           gene_id = unique(gene_cluster$gene_id), junction_category = "unknown", 
           transcript_isoforms = "unknown", junc_id = paste0("unk.", row_number())) %>%
    select(chr = chrom, junc_start = start, junc_end = end, everything()) %>%
    bind_rows(gene_cluster) %>%
    mutate(junc.counts = ifelse(is.na(cluster_idx), 0, junc.counts), cluster.counts = ifelse(is.na(cluster_idx), 0, cluster.counts)) %>%
    arrange(cluster_idx)

  n = all_gene_clusters %>% distinct(cluster_idx, junc_id) %>% group_by(cluster_idx) %>% 
    mutate(junc.per.cluster = ifelse(is.na(cluster_idx), 1, n())) %>% ungroup()

  all_gene_clusters %<>% left_join(n, by = c("cluster_idx", "junc_id")) %>%
    mutate(junc.usage = ifelse(junc.counts == 0, 0, round((junc.counts/cluster.counts)*100, digits = 0)), cell_line = paste0(cell_type))
  # end here

  top_guides = filtered_guides %>%
    group_by(junc_id) %>% slice_min(predicted_lfc, n = guides_per_junction) %>% ungroup()

  # make the isoforms shorthand- probably should change in original file
  output = top_guides %>% left_join(all_gene_clusters) %>%
    select(Cluster = cluster_idx, JuncID = junc_id, Category = junction_category, Counts = junc.counts, Usage = junc.usage,
           Isoforms = transcript_isoforms, GuideID = guide_id, GuideSeq = guide_sequence, Prediction = predicted_lfc)

@@

  return(nice_table(output, col.format.custom = 1:5, format.custom = "fun", 
                    title = paste0(gene_name, ": Top ", guides_per_junction, " gRNAs per Junction")))
}
